FTLR proof cases

### 2018-06-30 fully-abstract-comp/ftlr-proof-cases.tex
Discharge another TODO.

\begin{lemma}[Unique return seals]
  \label{lem:unique-ret-seals}
  If
  \begin{itemize}
  \item $\mscode([\aaddr..\aaddr+\calllen-1]) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$
  \item $\mscode([\aaddr'..\aaddr'+\calllen-1]) = \overline{\scall{\offpc',\offsigma'}{r_1'}{r_2'}}$
  \item $\mscode(\aaddr + \offpc) = \seal{\sigma_b,\sigma_e,\sigma_b}$ and $\sigma = \sigma_b + \offsigma$
  \item $\mscode(\aaddr' + \offpc') = \seal{\sigma_b',\sigma_e',\sigma_b'}$ and $\sigma = \sigma_b' + \offsigma'$
  \item $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode$
  \end{itemize}
  then
  \[
    \aaddr = \aaddr'
  \]
  and $\offpc = \offpc'$ and $\offsigma = \offsigma'$ and $r_1 = r_1'$ and $r_2 = r_2'$ and $\sigma_b = \sigma_b'$ and $\sigma_e = \sigma_e'$.
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}

>>>>

\begin{lemma}[Unique return seals]
  \label{lem:unique-ret-seals}
  If
  \begin{itemize}
  \item $\mscode([\aaddr..\aaddr+\calllen-1]) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$
  \item $\mscode([\aaddr'..\aaddr'+\calllen-1]) = \overline{\scall{\offpc',\offsigma'}{r_1'}{r_2'}}$
  \item $\mscode(\aaddr + \offpc) = \seal{\sigma_b,\sigma_e,\sigma_b}$ and $\sigma = \sigma_b + \offsigma$
  \item $\mscode(\aaddr' + \offpc') = \seal{\sigma_b',\sigma_e',\sigma_b'}$ and $\sigma = \sigma_b' + \offsigma'$
  \item $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode$
  \end{itemize}
  then
  \[
    \aaddr = \aaddr'
  \]
  and $\offpc = \offpc'$ and $\offsigma = \offsigma'$ and $r_1 = r_1'$ and $r_2 = r_2'$ and $\sigma_b = \sigma_b'$ and $\sigma_e = \sigma_e'$.
\end{lemma}
\begin{proof}
  From $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode$,
  we get a $d_\sigma : \dom(\mscode) \rightarrow \powerset{\Seal}$ such that the following holds:
  \begin{itemize}
  \item $\mscode$ has no hidden calls
  \item $\sigrets \mathrel{\#} \sigcloss$
  \item $\sigrets = \biguplus_{a \in \dom(\mscode)} d_\sigma(a)$
  \item $\forall a \in \dom(\mscode) \ldotp \sigrets,d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a$
  \item $\exists a \ldotp \mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\_} \wedge [\sigma_\baddr,\sigma_\eaddr] \neq \emptyset$
  \end{itemize}

  Particularly, we have $\sigrets,d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a$ and $\sigrets,d_\sigma(a'),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a'$.
  From these, and the facts that $\mscode([\aaddr..\aaddr+\calllen-1]) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ and $\mscode([\aaddr'..\aaddr'+\calllen-1]) = \overline{\scall{\offpc',\offsigma'}{r_1'}{r_2'}}$, it follows that
  \begin{itemize}
  \item $\mscode(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}$ and $\sigma_\baddr+\offsigma \in d_\sigma(a)$
  \item $\mscode(a'+\offpc') = \seal{\sigma_\baddr',\sigma_\eaddr',\sigma_\baddr'}$ and $ \sigma_\baddr'+\offsigma' \in d_\sigma(a')$
  \end{itemize}
  From the facts that $\sigma = \sigma_b + \offsigma = \sigma_b' + \offsigma'$, $\sigma_\baddr+\offsigma \in d_\sigma(a)$, $ \sigma_\baddr'+\offsigma' \in d_\sigma(a')$ and the disjointness of the $d_\sigma(a)$, we get that $a = a'$.
  With this fact, the rest of the proof obligations follow directly from the other assumed equations.
\end{proof}
